ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-07 rebuttal.tex

\begin{reviewer}
    %
    10.~Page 4, line 32: ``The second section of the file encodes the experimental data''. Perhaps
    it is easier to follow if this is briefly mentioned before the authors explain the details of
    the first section of the ChemKED format.
    %
\end{reviewer}

\begin{response}
    %
    We have updated the text on \textbf{page 4} to incorporate the suggested change.
    %
\end{response}

\begin{reviewer}
    %
    11.~Why do both \texttt{atomic-composition} and \texttt{elemental-composition} exist as
    synonyms? Wouldn't it be clearer if only one of the two can be used as a valid input?
    %
\end{reviewer}

\begin{response}
    We agree with the reviewer on this point, and have removed \texttt{elemental-composition}
    as an option for clarity. The text on \textbf{page 6} has been updated to reflect this.
\end{response}

@@

\begin{response}
    %

    %
\end{response}

\begin{reviewer}
    %
    13.~Page 6, line 12 describes the initial efforts of building an open repository of ChemKED
    files, on GitHub. Is this the most efficient way for making a publically available database? One
    issue with this is the fact that adding files is done via pull requests, which have to be
    verified and approved by the owners of the repository. Therefore a certain delay is inevitable.
    %
\end{reviewer}

\begin{response}
    %
    We agree that submitting files to the ChemKED database on GitHub will inevitably incur some
    delay, however we see the human intervention step as necessary and important. In much the same
    way that review of manuscripts provides a certain surety of the minimal quality of the article,
    we see review of data being added to the database as a minimal quality check; for instance, does
    the reference exist, has the data already been added to the database, are the files styled
    consistently, etc. Furthermore, such human review can help to catch some errors that may be
    introduced by manual creation of the files, as pointed out by the reviewer previously.

    All the existing database have a similar requirement, where users submit
    data files for inclusion that are approved by the database owners after some review. In this
    sense, we actually see the Pull Request mechanism of GitHub as an advantage, since all reviews
    can be done publicly and some of the review procedures (style checks, reference validity, etc.)
    may be done automatically by a script associated with the GitHub repository. In this way, the
    entire community can contribute to improving the quality of the database.

    Lastly, while we hope other researchers will contribute to this database (such that it becomes
    more of a community effort than our effort), there is no requirement for others to use our
    database to use ChemKED files or PyKED. Others are free to use the tools internally, or
    download\slash fork our database and build their own.
    %
\end{response}

### 2017-10-07 rebuttal.tex

    All the existing database have a similar requirement, where users submit
    data files for inclusion that are approved by the database owners after some review. In this
    sense, we actually see the Pull Request mechanism of GitHub as an advantage, since all reviews
    can be done publicly and some of the review procedures (style checks, reference validity, etc.)
    may be done automatically by a script associated with the GitHub repository. In this way, the
    entire community can contribute to improving the quality of the database.

    Lastly, while we hope other researchers will contribute to this database (such that it becomes
    more of a community effort than our effort), there is no requirement for others to use our
    database to use ChemKED files or PyKED. Others are free to use the tools internally, or
    download\slash fork our database and build their own.
    %
\end{response}

\begin{reviewer}
    %
    14.~Page 6, line 18 states that a converter exists from ReSpecTh to ChemKED. But isn't this
    feature added when going from v0.1.6 to v0.2.0, which makes page 3 line 21: v0.1.6 not correct.
    %
\end{reviewer}

\begin{response}
    %
    In principle, the version of the ChemKED database format and the version of the PyKED Python
    package are entirely independent. Thus, since adding the converters incurred no changes to the
    database format, the description of the format in the manuscript is a description of v0.1.6,
    which happens to be identical to v0.2.0. However, in practice, the versions of PyKED and the
    ChemKED database have been coupled up to now, and we have updated the version mentioned in the
    text on \textbf{page 3} to vX.X.X, which we released in conjunction with submitting
    this response after the helpful comments of the reviewers.
    %
\end{response}

### 2017-10-07 pyked.tex
made all section names sentence case

%====================================================================
\section{Overview of ChemKED format}\label{sec:overview-of-format}

@@

\subsection{Apparatus Information and Metadata}\label{sec:apparatus-information-and-metadata}

@@

\subsection{Ignition Delay Experimental Data}\label{sec:ignition-delay-experimental-data}

@@

\subsubsection{Shock Tube Experiments}\label{sec:shock-tube-experiments}

@@

\subsubsection{Rapid Compression Machine Experiments}\label{sec:rcm-experiments}

@@

\subsection{Public Database of \ck{} Files}\label{sec:public-database}

@@

%====================================================================
\section{PyKED Architecture}\label{sec:pyked-architecture}
%
\pk{} is a Python package that provides the reference implementation
of the interface to \ck{} files~\autocite{PyKED}. \pk{} reads \ck{} files, validates
their structure and content, and allows the user to interact with the data contained
in the \ck{} file.

@@

%====================================================================
\section{Usage examples}\label{sec:usage-example}

@@

\subsection{RCM modeling with varying reactor volume}\label{sec:rcm-modeling}

@@

\subsection{Shock tube modeling with constant volume}\label{sec:shock-tube}

>>>>

%====================================================================
\section{Overview of ChemKED format}
\label{sec:overview-of-format}

@@

\subsection{Apparatus information and metadata}
\label{sec:apparatus-information-and-metadata}

@@

\subsection{Ignition delay experimental data}
\label{sec:ignition-delay-experimental-data}

@@

\subsubsection{Shock tube experiments}
\label{sec:shock-tube-experiments}

@@

\subsubsection{Rapid compression machine experiments}
\label{sec:rcm-experiments}

@@

\subsection{Public database of \ck{} files}
\label{sec:public-database}

@@

%====================================================================
\section{PyKED architecture}
\label{sec:pyked-architecture}
%
\pk{} is a Python package that provides the reference implementation
of the interface to \ck{} files~\autocite{PyKED}. \pk{} reads \ck{} files, validates
their structure and content, and allows the user to interact with the data contained
in the \ck{} file.

@@

%====================================================================
\section{Usage examples}
\label{sec:usage-example}

@@

\subsection{RCM modeling with varying reactor volume}
\label{sec:rcm-modeling}

@@

\subsection{Shock tube modeling with constant volume}
\label{sec:shock-tube}
